ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-25 pyked.tex
Add Pandas reference

\pk{} relies on well-established scientific Python software tools. These include
NumPy~\autocite{vanderWalt:2011np} for array manipulation,
Pint~\autocite{Grecco2016} for interpreting and converting between units,
\texttt{ruamel.yaml}~\autocite{ruamel_yaml} for parsing YAML files, Cerberus for
validating \ck{} files~\autocite{cerberus}, and pytest~\autocite{pytest:3.0.1}
for unit testing. Travis-CI~\autocite{Travis2016} provides continuous
integration testing.

>>>>

\pk{} relies on well-established scientific Python software tools. These include
NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010} for
array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, \texttt{ruamel.yaml}~\autocite{ruamel_yaml} for parsing YAML
files, Cerberus for validating \ck{} files~\autocite{cerberus}, and
pytest~\autocite{pytest:3.0.1} for unit testing. Travis-CI~\autocite{Travis2016}
provides continuous integration testing.
